Temporal trends (NAMCS)

### 2017-07-07 ms1/namcs_trends.Rmd
cleanup namcs trend

g = function(design) {
  lapply(top_abx$abx, function(x) f(design, x)) %>% bind_rows() %>%
    left_join(census, by='year') %>%
    mutate(apc=n_abx/n_total, se=se/n_total)
}

abx_time = g(design)
abx_time_adult = g(adult_design)
```

@@

### Levo trend

```{r levo_ratio}
levo_time = abx_time %>%
  filter(abx=='levo') %>%
  arrange(year)

@@

>>>>

g = function(design, denom) {
  lapply(top_abx$abx, function(x) f(design, x)) %>% bind_rows() %>%
    left_join(census, by='year') %>%
    rename_(.dots=setNames(denom, 'denom')) %>%
    mutate(apc=n_abx/denom, se=se/denom)
}

abx_time = g(design, 'n_total')
abx_time_adult = g(adult_design, 'n_adult')
```

@@

## Trends among the adults

I do the same analysis, but just among adults. Weirdly, the results look a lot
different. The confidence intervals get a lot bigger.

```{r adult_trends}
adult_models = abx_time_adult %>%
  group_by(abx) %>%
  do(tidy(lm(apc ~ year, weight=1.0/se^2, data=.))) %>%
  ungroup()

adult_models %>%
  filter(term=='year') %>% select(-term) %>%
  mutate(ci=1.96*std.error, ymin=estimate-ci, ymax=estimate+ci) %>%
  mutate(abx=forcats::fct_reorder(abx, estimate)) %>%
  ggplot(aes(x=abx, y=estimate, ymin=ymin, ymax=ymax)) +
  geom_point() + geom_linerange() +
  coord_flip() +
  theme_minimal()
```

### Just levo

```{r levo_ratio}
levo_time = abx_time_adult %>%
  filter(abx=='levo') %>%
  arrange(year)

@@

```{r}
levo_time %>%
  select(year, abx_per_capita=apc, se) %>%
  kable
```
